COG-ED Manuscript

### 2022-02-15 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd

@@

# Methods

The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated using the *BayesFactor* package [@Morey2021].

@@

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).

>>>>

  <!-- papaja must be installed from GitHub so code above will not work for this package-->
  # Install devtools package if necessary
  # if(!"devtools" %in% rownames(installed.packages())) install.packages("devtools")

  # Install the stable development verions from GitHub
  # devtools::install_github("crsh/papaja")

  # Install the latest development snapshot from GitHub
  # devtools::install_github("crsh/papaja@devel")

@@

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *bayestestR* [@Makowski2019] for all our analyses.

@@

The results of each analysis will be assessed on the basis of both $p$-value and the Bayes factor $BF10$, calculated with the *BayesFactor* package [@Morey2021] using the default prior widths of the functions *anovaBF*, *lmBF* and *regressionBF* corresponding. <!-- hoffe, das reicht denen, denn wenn man genauer werden will, müsste man noch zwischen fixed und random effects priors unterscheiden, die zu allem Überdruß auch noch unterschiedliche Zahlenwerte haben, 1/2 für fixed und 1 für random bei anovaBF und lmBF, aber sqrt(2)/4 bei regressionBF -->

@@

The paradigm code as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).
